\section{Useful information for parents (-to-be)}

\subsection{What you Need to know about Maternity Leave?}

\href{http://wwwen.uni.lu/university_newsletter/newsletter_system/hr_spotlight/hr_spotlight_all_you_need_to_know_about_maternity_and_parental_leave/what_you_need_to_know_about_parental_leave}{What you Need to know about Parental Leave?}

More info:
Parents in Luxembourg have the right to an additional month of parental leave and can request more flexible working arrangements under a new law.
 
The main points of the law are as follows:
\begin{itemize}
	\item The first parental leave has to immediately follow maternity leave. If parents fail to make an application on time, but otherwise meet all conditions, they can now receive four months of unpaid leave, up from three months under the old law.
	\item Parents from the private or public sector have the right to ask their employer to amend their schedule to allow for more flexible working hours during a period of up to one year. The employer must consider the request and respond in light of the company's needs and those of the applicant. Any request rejections must be justified.
\end{itemize}

Source: \href{http://www.wort.lu/en/view/new-parental-leave-law-explained-51935346e4b0889d25ec2b91}{New parental leave law explained}
 
\subsection{Support for family (in French)}

\noindent \href{http://www.guichet.public.lu/citoyens/fr/index.html}{www.guichet.public.lu}
 
\noindent \href{http://www.guichet.public.lu/citoyens/fr/famille/index.html}{Famille}
 
\noindent \href{http://www.guichet.public.lu/citoyens/fr/famille/parents/index.html}{Parents}


\subsection{Gynaecology and obstetrics Doctors}
For example, Schmit Alix (Dr), \
\href{http://goo.gl/i4Dw3k}{43 All\'ee L\'eopold Goebel, L-1635 Luxembourg}, Tel.: \href{callto:44 91 88}{44 91 88} \\
Dr. Paul Gratia (Tel.: \href{callto:26 97 68 86 1}{26 97 68 86 1}) or Dr. Claude Borsi (Tel.: \href{callto:45 46 30 1}{45 46 30 1}), 45-47 rue de Aubepines, L-1145 Luxembourg\\
More: \url{http://www.yellow.lu/en/directory/by-categories/health-beauty/gynecology-and-obstetrics}\\
Or \url{http://www.collegemedical.lu/Scripts/sql.exe?SqlDB=CM&Sql=Default.phs}
 
Note:
Please keep in mind that this document does not represent an official position and it is selective by its nature.
Some info could be obsolete, please check and also keep it updated for others by sending feedback to the SPA's representatives. 