\section{Finding an accommodation}
If you are a PhD student that only needs a single accommodation, you may want to apply for a student accommodation offered by the university. Please apply as early as possible because the number of this kind of accommodation is very limited.
\url{http://wwwen.uni.lu/students/accommodation}. 

If you are a postdoc, you can not apply for a student accommodation. 
But you can ask SEVE, email: \href{mailto:seve.logement@uni.lu}{seve.logement@uni.lu} if they have some temporary accommodation (even for your family) before you can find one for yourself. 
The rooms for family are only for 3 months maximum.
 
If you come with your family, the university does not have accommodation support yet in this case. You may want to find an apartment from the free market. 

WARNING: Frauds in private ads do exist! There are (rare but existed) some cases that we are aware of some people lost the deposit money to a non-existing flat. So the key point to remember is that please don't transfer the deposit in advance but only when signing the contract after having visited the flat. 

Be aware that there could be more flats, apartments, etc. available for rent at some periods like around summer/autumn. 
That means in some period like during winter, there could be much less options of to choose, and finding a suitable accommodation even more difficult. 
Thus, if you plan to arrive in Luxembourg during winter time, keep that in mind and better search for accommodation as soon as possible. 

These sites are quite helpful to find your new home:
\begin{itemize}
	\item \url{http://www.athome.lu/}
	\item \url{http://www.habiter.lu/}
	\item \url{http://www.immotop.lu/}
	\item \url{http://www.immostar.lu/v8/}
	\item \url{http://www.immofinder.lu/}
	\item \url{http://www.guideimmobilier.lu/}
	\item \url{www.luxbazar.lu}
\end{itemize}

Most of the offers are from the agency but some are still posted by the owners, without the agency fee.
You may find out by scanning them carefully. 

TIP: Once you have decided to rent a flat, it could be better to ask the contact person at your bank in Luxembourg to create the bank guarantee to be used as deposit for the landlord. 
With the bank guarantee, you don't have to give the deposit fee to the landlord in cash. 
It could be more convenient to get back the deposit after finishing your renting contract. 

Flat sharing could be cheap if divided by the number of flatmates:
\begin{itemize}
\item \url{http://www.luxfriends.eu/}
\item \url{http://www.lesfrontaliers.lu/annonces-immobilieres}
\item \url{http://www.furnished.lu} 
\item \href{http://fr.welchome.com/flateshare-houseshare/LU-Luxembourg/luxembourg?oa_code=99501330}{Accommodation in Luxembourg} 
\end{itemize}

There are also some pages where you can find mostly apartments for rent without the agency fee.
\begin{itemize}
	%\item \url{http://www.lesfrontaliers.lu/petites-annonces/1/Immobilier/recherche}
	\item \href{http://www.diegrenzgaenger.lu/index.php?p=annonce&a=srub&id=10}{diegrenzgaenger.lu}
	\item \href{http://luxembourg.angloinfo.com/classifieds/index/1003-1005-1004-1010/category/residential-property/}{Residential Property}
	\item \href{http://www.justlanded.com/english/Luxembourg}{Living, working or studying in Luxembourg?}
	\item \href{http://www.luxbazar.lu}{luxbazar.lu}
\end{itemize}

Please also look out for announcements in local newspapers like Tageblatt and Wort.
You can also contact us, the SnT PhD student Association (SPA), and we can try to help you with our personal networks. 

WARNING: You should have a renting contract, check the status of the room carefully, take photos before moving in. 
This could help you to avoid some problems in getting your deposit money back after finish the rent. 

\subsubsection{Luxembourg Hostel Reservation:} Note that if you need to find some temporary place to stay while searching for your long-term accommodation, you may choose Youth Hostels in Luxembourg. Hostels in Luxembourg, \url{http://www.youthhostels.lu/} are very good in terms of quality w.r.t. the price. Even though they are called Youth Hostels but there is NO age limit.
To book the Luxembourg City-Hostel, please click on the following link: \href{http://youthhostels.lu/en/youth-hostels/youth-hostel-luxembourg}{Youth Hostels: Luxembourg}

\subsubsection{Declaration of arrival at the commune: } Within three working days from the date of entering the country, you should go to the commune authorities in the place of your stay to make a declaration of arrival. 
You need to make a declaration of arrival every time you change your home address in Luxembourg. 

\subsubsection{Getting an Internet and telephone provider, electricity provider:} Once you have signed the housing contract, the next step could be finding an internet and telephone provider. 
Some big ISPs in Luxembourg: \url{http://www.providers.lu}. 
For the electricity contract, your housing agency or the renter should give you information about this. 

\subsubsection{SnT Welcome-buddy Programme:} The SnT welcome-buddy programme is supposed to match newcomers with people at SnT who already have some experiences of living in Luxembourg in order to facilitate the very first weeks after the arrival of newcomers. 
These matchings are intended for a short period of time (e.g. during the first week) so that a newcomer can have a specific person to ask for information/help, and of course you and your welcome-buddy can maintain this relationship as long as you two want. 

%This programme is not officially started yet and there will be some trials first. 
If you are a newcomer who would like to have a welcome-buddy at SnT, please send us a request by email. 
If you have been living in Luxembourg for a while and are willing to help newcomers at SnT when they just arrive, please subscribe to the list of welcome-buddies by emailing the SPA's representatives. 

%The first two sections about Traveling to Luxembourg and Finding an accommodation in Luxembourg are two of the most important things you mostly want to know before arriving in Luxembourg. In fact, the Luxembourg government does provide official documents, i.e. guide-euraxess and JustArrived, that contain lots more official information as you can see from the two following sections.
