\section{On-going Activities within SPA} \label{sec_activities}
There are always some activities within SPA driven by interests of our members. 
For each activity, there is a working group that manage and support for that activity. 
Anyone can propose an activity that could benefit also other members of SPA, and SnT in general. 
Please contact the SPA's representatives for anything related to the activities. 

The following groups are active within SPA. If you have questions or want to participate feel free to contact the SPA's representatives or anyone in the working groups. 
SPA is thankful to have all the people who have joined a working group and hope to have more volunteers to join/create working groups. 

\subsection{SPA's Handbook}

This document (the handbook) itself is one of the key activities within SPA. 
The handbook is for sharing experiences and also representing all main activities in our association. 
As can be seen in the abstract, the handbook provides some practical information about working and living in Luxembourg for newcomers joining SnT. 
It is not an official document. 
The handbook needs to be kept up-to-date and improved all the time. 
Ideally, its content should be contributed by everyone to validate and update the info. 

The handbook is managed by the SPA's representatives and the working group of Diego Kreutz, Christian Hammerschmidt, Reza Matinnejad and Phu-Hong Nguyen. 
The \href{https://github.com/SPAlux/handbook}{latex source files} are available on github. 


The working group will react to pull requests, or suggestions via email. 
Please contribute to this document!
 
\subsection{Language Lunches}
Please refer to Section \ref{lbl_langlunch} for an introduction about this activity. 
Currently we have German speaking lunch on Thursday noon and French speaking lunch on Friday noon. 
For more details, please contact the SPA's representatives. 
 
\subsection{Sport}
Please refer to Section \ref{sec_sport}. 

\subsection{Game Night}
Walter and Thierry are organising game events. 
Normally there are many funny group games, not video games. 
If you want to help out, suggest games or contribute in another way, please email anyone in the working group.

\subsection{Networking Drink, BBQ, and/or SnT Food Day}
Currently, SPA together with LuxDoc are co-organizing the NetworkingDrink events where one can meet other young researchers in Luxembourg and more than that!
Come and see who you might meet there! 
Save the date! every 3rd Thursday monthly (only some special events like Summer BBQ would be on another date). 
Location and time to meet will be communicated 1 week before the event, and also can be found in this page: \href{https://www.facebook.com/pages/LuxDoc-ASBL/275000555887801}{https://www.facebook.com/pages/LuxDoc-ASBL/275000555887801}

SPA may occasionally organize some BBQ event for all SnTers, e.g. in Spring or Summer. 
Currently, Diego and Thierry are in charge, but volunteers are needed to help. 
SPA's members are also active in organizing and/or participating in the annual SnT Food Day in December. 


\subsection{Toastmasters}
About public speaking and leadership skills, sometimes SPA organizes Toastmasters demo meetings at SnT with the help from a great Toastmasters club in Luxembourg: the Casemates. 
This event is also on demand only. 
But you can always participate in a real Toastmasters meeting in a club in Luxembourg, for free!
Interested? check out the website of some Toastmasters Clubs in Luxembourg:  \href{http://tmclub.eu/portal.php?marknow=0}{http://tmclub.eu/portal.php?marknow=0}

\subsection{Cross-Organization Activities}
SPA may also organize some activities together with other associations. 
Currently we have some common interests with some organizations like \href{http://LuxDoc.org}{LuxDoc}, \href{http://servethecity.lu/}{ServeTheCity}, etc. 
Any suggestion about cross-org activities are more than welcome. 

\subsection{Traveling Lovers}
This is still an idea and need people to make it active! 
The idea is to group SnTers who are interested in visiting nearby cities around Luxembourg and neighbor countries. 
Not only cities visiting but other similar activities like hiking, skiing, etc. are also welcome. 

\subsection{SPA Newsletter}
This is still an idea because SPA is looking for one or two volunteers who can be the editor(s) of the SPA Newsletter. 
The role of a editor is to collect reports from different SPA's activities and edit a newsletter (every two or three months) about SPA's activities. 
If you are interested in helping us, please contact the SPA representatives. 