\section{Introduction}
\label{sect.intro}


The main ideas and structure of this document are presented in Section \ref{ssec_about}. 
This document is created to realise some of the main objectives of the SnT PhD Student Association shown in Section \ref{ssec_SPA}. 
Section \ref{ssec:revisions} keeps track of all the changes that were made in the major versions of this document. 

\subsection{About this document} \label{ssec_about}
Welcome to Luxembourg and SnT! We hope that you will enjoy living in a beautiful country and working at our research centre SnT. Moving from one country to live and work in another country is a great experience but in many cases it is also challenging. For example, which paperwork has to be done once you have just arrived in Luxembourg? how to find a suitable accommodation? etc. 

This document is prepared by the SnT PhD student Association (shortly called SPA\footnote{If you like Spa, just call it so :D}) in order to provide more information about working and living in Luxembourg for newcomers at SnT. Hopefully it could provide you some useful information that you may use to settle down asap in Luxembourg. The practical information will be presented in an order that you may want to follow, from before arriving in Luxembourg to settling down in your new accommodation in Luxembourg. 
The content of this document is not only based on some official documents, like Euraxess \cite{Euraxess}, Just Arrived \cite{JustArrived}, or less formal source like AngloInfo \cite{AngloINFO}, but also based on the actual experiences of people at our research centre. 

This document will be kept up-to-date by people in our research centre with their new experiences so it would be useful for not only newcomers! 
After living in Luxembourg for a while, if you have some good (or bad!) experiences to share, please let us know. 
We will include your experiences in the next versions of this document. 
For further information, please feel free to contact the representatives of SPA that can be found on the SPA's website. 

\subsection{About the SnT PhD student Association (SPA)}
\input{text/SPA.tex}

\subsection{Revisions}
\input{text/revisions}