\section{Traveling to Luxembourg/SnT}

\subsubsection{Traveling to Luxembourg: }
On how to get to Luxembourg, e.g. by airplane, train, etc. , you can find some useful guide on this page:
\href{http://www.icst.lu/site/icst2013/location-travel/travel}{Traveling to Luxembourg}. 
 
\subsubsection{The local public transportation system: }
Once you have just arrived in Luxembourg, it's good to know the public transportation system in the country. It's very convenient to use! For moving with public transport in the city and country of Luxembourg, you may use the website \href{http://mobiliteit.lu}{mobiliteit.lu}: \href{http://travelplanner.mobiliteit.lu/hafas/cdt/query.exe/en?}{PLANIFIER un parcours}
 
Note that for PhD students, while doing (re-)enrollment for every new semester, it’s possible to register and buy a student travel ticket costs only EUR 37.5 for the whole academic semester! Then, you can use the public transportation to travel unlimited in the whole country. So, remember to register for it when you are doing the (re-)enrollment at every new semester.

\subsubsection{Opening a bank account: } 
This is one of the first things you would need to do once you arrive in Luxembourg. 
Without a bank account, many other things are difficult to be done. 
Nicely, the university has agreements with some banks in Luxembourg, i.e. the \href{https://www.bcee.lu/}{National Bank (BCEE)} and the \href{https://www.bil.com/en/individuals/Pages/default.aspx}{International Bank in Luxembourg (BIL)}. 
Therefore, you can open your bank accounts in these banks without any fee (note to bring your work contract and your documents). 